J-Study supplement

### 2023-07-30 writing/supplement.Rmd
remove figs actually, rename file

---
title: "J-Study manuscript"
author: "Monica Thieu"
date: "Updated `r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
require(targets)
require(tidyverse)
require(magrittr)
require(rlang)
# source(here::here("R", "get_cleaned_data.R"))
# load(here::here("ignore", "data", "preplots.rda")) # For the model params
# load(here::here("ignore", "data", "plots_ms.rda"))

target_store <- here::here("ignore", "_targets")
signif_digits <- 3L
```

```{r setup-extra-stat-reports}
summarize_kable <- function (data,
                               col,
                               digs = signif_digits,
                               fn_list = list(mean = \(x) mean(x, na.rm = T),
                                              sd = \(x) sd(x, na.rm = T))) {
  data %>% 
    summarize(across({{col}}, fn_list)) %>% 
    mutate(across(where(is.numeric), \(x) signif(x, digits = digs))) %>% 
    knitr::kable()
}
```

# Figures and captions

## Figure 3

```{r}
q_google_demos <- tar_read(q_google_demos, store = target_store)
j_exp <- tar_read(expertise_summarized, store = target_store)
plot_demos <- tar_read(plot_demos, store = target_store) +
  theme_ms +
  theme(legend.position = c(1, 1),
          legend.justification = c(1, 1)) 
plot_expertise_hist <- tar_read(plot_expertise_hist, store = target_store) +
  theme_ms
```

```{r figure-3}
knitr::include_graphics(here::here("ignore", "figs", "ms_fig3.png"))
```

## Figure 4

```{r}
knitr::include_graphics(here::here("ignore", "figs", "ms_fig4.png"))
```

## Figure 5

```{r}
knitr::include_graphics(here::here("ignore", "figs", "ms_fig5.png"))
# Question from Chris at Alyssano CNS practice lab meeting March 10 2023: Were trivia experts more likely to report certain facts as novel? (like, ones that might be harder)
```

@@

@@

```{r}
j_exp %>% 
  # to get it in units of questions
  mutate(j_score = j_score * 50) %>% 
  summarize_kable(j_score,
                  fn_list = list(min = \(x) min(x, na.rm = T),
                                 max = \(x) max(x, na.rm = T),
                                 median = \(x) median(x, na.rm = T)))
```

@@

```{r}
preplot_fixef_fact_by_both %>% 
  group_by(j_score, resp_pic, resp_source) %>% 
  summarize_kable(acc_pred,
                  fn_list = list(median = median))
```

>>>>

---
title: "J-Study supplement"
author: "Monica Thieu, Lauren Wilkins, & Mariam Aly"
date: "Updated `r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
require(targets)
require(tidyverse)
require(magrittr)
require(rlang)

target_store <- here::here("ignore", "_targets")
signif_digits <- 3L

summarize_kable <- function (data,
                               col,
                               digs = signif_digits,
                               fn_list = list(mean = \(x) mean(x, na.rm = T),
                                              sd = \(x) sd(x, na.rm = T))) {
  data %>% 
    summarize(across({{col}}, fn_list)) %>% 
    mutate(across(where(is.numeric), \(x) signif(x, digits = digs))) %>% 
    knitr::kable()
}
```

@@

```{r}
q_google_demos <- tar_read(q_google_demos, store = target_store)
```

@@

```{r}
j_exp <- tar_read(expertise_summarized, store = target_store)

j_exp %>% 
  # to get it in units of questions
  mutate(j_score = j_score * 50) %>% 
  summarize_kable(j_score,
                  fn_list = list(min = \(x) min(x, na.rm = T),
                                 max = \(x) max(x, na.rm = T),
                                 median = \(x) median(x, na.rm = T)))
```

@@

```{r}
tar_read(preplot_fixef_fact_by_both, store = target_store) %>% 
  group_by(j_score, resp_pic, resp_source) %>% 
  summarize_kable(acc_pred,
                  fn_list = list(median = median))
```
